---
title: "ASHA 2023 Listening Effort Data Analysis"
author: "Micah E. Hirsch"
date: "2023-10-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose

```{r, include = F, warning = F, message = F}

# Load Needed Packages
library(rio) # install.packages("rio")
library(tidyverse) # install.packages("tidyverse")
# Need remotes package to install gazer and saccades
library(remotes) # install.packages("remotes")
library(gazer) # remotes::install_github("dmirman/gazer")
library(saccades) # remotes::install_github("tmalsburg/saccades/saccades")
library(zoo) # install.packages("zoo")
library(ggpubr)
library(gt) # install.packages("gt")

```

# Descriptive Statistics

## Participant Demographics

First, we will present the demographics of our listeners To date, we recruited 20 listeners to participate in the study. Three listeners were removed from the analysis. One listener decided to withdraw from the study, so their data was removed from the database. For the other two participants, pupillometry data was either not recorded or lost due to instrumental issues. Therefore, for this analysis, we have 17 participants. The descriptive information for these participants are presented below. 

```{r}

# Load in dataset for listener demographics

listener_demo <- rio::import("Cleaned Data/cleaned_listener_demo.csv") 

```

## Phrase Accuracy



```{r}

# Load in cleaned data 

data <- rio::import("Cleaned Data/cleaned_data.csv")

# Selecting relevant variables to explore phrase accuracy and perceived listening effort
data1 <- data %>%
  dplyr::select(subject, trial, speaker, effort_rating, rep_acc) %>%
  dplyr::distinct() %>%
  # removing trials with missing rep accuracy: 3 trials removed
  dplyr::mutate(rep_acc = ifelse(rep_acc == "", NA, rep_acc)) %>%
  dplyr::filter(!is.na(rep_acc))

# Calculating repetition accuracy descriptive data

rep_acc <- data1 %>%
  dplyr::group_by(speaker, rep_acc) %>%
  dplyr::summarize(n = n())

```



## Perceived Listening Effort Ratings



