---
title: "Exploratory Figures"
author: "Micah E. Hirsch"
date: '`r Sys.Date()`'
output:  
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose

The purpose of this document is to conduct and create a few exploratory analyses and figures. These analyses are unplanned and not part of the main study, but were mainly created to include in M. Hirsch's dissertation defense.

```{r}

library(rio) # install.packages("rio")
library(tidyverse) # install.packages("tidyverse")
library(mgcv) # install.packages("mgcv")
library(itsadug) # install.packages("itsadug")
library(ggpubr) # installl.packages("ggpubr")
library(gt) # install.packages("gt")
library(gtsummary) # install.packages("gtsummary")
library(glmmTMB) # install.packages("glmmTMB")
library(performance) # install.packages("performance")
library(sjPlot) # install.packages("sjPlot")
library(viridis) # install.packages("viridis")

```


# Listening Effort and Intelligibility

## Pupil Dilation


```{r}

phrase_acc <- rio::import("Cleaned Data/repetition_accuracy.csv") |>
  dplyr::select(subject, trial, targetphrase, initial_response, target_number, correct_words_initial, rep_acc) |>
  dplyr::mutate(rep_acc = ifelse(initial_response == "missing data", NA, 
                                 ifelse(target_number == correct_words_initial, "accurate", "inaccurate")),
                intel = (correct_words_initial/target_number) * 100) |>
  dplyr::select(!c(targetphrase, initial_response))

pupil_df <- rio::import("Cleaned Data/cleaned_pupil_data_normalized.csv") |>
  # Merging phrase accuracy information with df
  dplyr::left_join(phrase_acc, by = c("subject", "trial")) |>
  # Filter out trials with missing phrase repetition data 
  dplyr::filter(!is.na(rep_acc)) |>
  dplyr::mutate(speaker = factor(speaker, levels = c("Control", "ALS")),
                rep_acc = factor(rep_acc, levels = c("accurate", "inaccurate")),
                phrase = as.factor(code),
                listener = as.factor(subject),
                trial_c = trial - 6) |>
  dplyr::group_by(listener, speaker) |>
  dplyr::mutate(num_points = n()) |>
  dplyr::mutate(start_event = c(TRUE, rep(FALSE, each = (num_points - 1)))) |>
  ungroup()

```

```{r}

intel_pupil <- bam(normed_pupil ~ speaker +
                  s(time_norm, by = speaker, k = 10) +
                  te(time_norm, intel, k = 10) +
                  # Random Smooth for listener
                  s(time_norm, listener, bs = 'fs', m =1),
                discrete = T,
                family = "scat",
                AR.start = start_event,
                rho = .9341941,
                data = pupil_df)

# summary.gam(intel_pupil)

gam.check(intel_pupil)

acf_resid(intel_pupil)

```

```{r}

df_pred <- expand_grid(
  time_norm = seq(from=min(pupil_df$time_norm), 
              to=max(pupil_df$time_norm), 
              length.out = 100),
  intel = seq(from=min(pupil_df$intel), 
              to=max(pupil_df$intel), 
              length.out = 100),
  speaker = c("Control", "ALS"),
  listener = c("LE01", "LE02", "LE04", "LE05", "LE06", "LE07", "LE08", "LE09", "LE10", "LE11",
               "LE12", "LE13", "LE15", "LE16", "LE18", "LE19", "LE20", "LE21", "LE22", "LE23",
               "LE24", "LE25", "LE26", "LE27", "LE28", "LE29", "LE30", "LE31", "LE32", "LE33", 
               "LE34", "LE35", "LE36", "LE38"))

df_pred <- predict(intel_pupil, newdata = df_pred, 
                      se.fit = TRUE) |> 
  as_tibble() |>
  cbind(df_pred)

df_pred |>
  dplyr::mutate(speaker = factor(speaker, levels = c("Control", "ALS"),
                                   labels = c("Neurotypical", "ALS"))) |>
  dplyr::filter(time_norm >= 0 & time_norm <= 5000) |>
  ggplot() +
  aes(x = time_norm,
      y = intel,
      group = speaker) +
  geom_tile(aes(fill = fit)) +
  geom_contour(aes(z = fit), colour = "white") +
  facet_wrap("speaker") +
  theme_classic() +
  labs(fill = "Pupil Dilation Estimate",
       x = "Normed Time (ms)",
       y = "Intelligibility (% Words Correct)") +
  scale_fill_viridis(option = "D") +
  theme(aspect.ratio = 1,
        legend.position = "bottom",
        axis.line = element_blank(),
        axis.text.x = element_text(angle = 45, hjust=1))

ggsave("Figures/intel_heatmap.png", plot = last_plot())

```

## Peak Pupil Dilation

### LME Model

```{r}

peak_pupil <- pupil_df |>  
  dplyr::filter(time_norm >= 500) |>
  dplyr::group_by(subject, trial) |>
  # filtering out timebins 1000 ms after phrase offset
  dplyr::filter(time_norm<= max(time_norm) - 2000) |>
  dplyr::ungroup() |>
  # Getting Peak Pupil Dilation Value
  dplyr::group_by(subject, trial, speaker, code, intel) |>
  dplyr::summarize(peak_pupil = max(normed_pupil)) |>
  dplyr::ungroup() |>
  dplyr::mutate(trial_c = trial - 6)

peak_pupil_model <- glmmTMB(peak_pupil ~ intel*speaker + (1|subject), data = peak_pupil)
#summary(peak_pupil_model)

peak_pupil_model_2 <- glmmTMB(peak_pupil ~ poly(intel, degree = 2)*speaker + (1|subject), data = peak_pupil)
#summary(peak_pupil_model_2)

anova(peak_pupil_model, peak_pupil_model_2)

sjPlot::tab_model(peak_pupil_model, peak_pupil_model_2,
                  file = "Tables/peak_pupil_intel_model.html")

```

### Plot

```{r}

peak_pupil |>
  dplyr::mutate(speaker = factor(speaker, levels = c("Control", "ALS"),
                                   labels = c("Neurotypical", "ALS")),
                color = ifelse(speaker == "ALS", my_pal[5], my_pal[1])) |>
  ggplot() +
  aes(x = intel,
      y = peak_pupil,
      color = speaker) +
  geom_line(method = "lm", stat = "smooth", aes(group = subject), alpha = .3) +
  geom_line(stat = "smooth", method = "lm", size = 2) +
  labs(x = "Intelligibility (% Words Correct)", 
       y = "Peak Pupil Dilation (Arbitrary Units",
       color = "Speaker", fill = "Speaker", linetype = "Speaker", shape = "Speaker") +
  facet_wrap("speaker") +
  theme_bw() +
  theme(legend.position = "bottom",
        aspect.ratio = 1) +
  coord_cartesian(ylim = c(0, 850)) +
  scale_color_manual(values = c(my_pal[1], my_pal[5]))

ggsave("Figures/pupil_intel.png", plot = last_plot())

```


## Perceived Listening Effort (PLE) Ratings

### LME Model

```{r}

ple_data <- rio::import("Cleaned Data/cleaned_ple_data.csv") |>
  dplyr::left_join(phrase_acc, by = c("subject", "trial")) |>
  dplyr::mutate(speaker = factor(speaker, levels = c("Control", "ALS")),
                trial_c = trial - 6,
                rep_acc = factor(rep_acc, levels = c("accurate", "inaccurate"))) |>
  dplyr::filter(!is.na(rep_acc)) |>
  dplyr::filter(effort_rating > 0)

ple_model <- glmmTMB(effort_rating ~ intel*speaker +
                       (trial_c|subject) + (trial_c|code), data = ple_data)
summary(ple_model)

```

### Plot

```{r}

ple_data |>
  dplyr::mutate(speaker = factor(speaker, levels = c("Control", "ALS"),
                                   labels = c("Neurotypical", "ALS")),
                color = ifelse(speaker == "ALS", my_pal[5], my_pal[1])) |>
  ggplot() +
  aes(x = intel,
      y = effort_rating,
      color = speaker) +
  geom_line(method = "lm", stat = "smooth", aes(group = subject), alpha = .3) +
  geom_line(stat = "smooth", method = "lm", size = 2) +
  labs(x = "Intelligibility (% Words Correct)", 
       y = "Peak Pupil Dilation (Arbitrary Units",
       color = "Speaker", fill = "Speaker", linetype = "Speaker", shape = "Speaker") +
  facet_wrap("speaker") +
  theme_bw() +
  theme(legend.position = "bottom",
        aspect.ratio = 1) +
  coord_cartesian(ylim = c(0, 7)) +
  scale_color_manual(values = c(my_pal[1], my_pal[5]))

ggsave("Figures/ple_intel.png", plot = last_plot())

```

# Correlations between Peak Pupil Dilaiton and PLE Ratings

```{r}



```

